Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-16 paper/paper.tex
Change instances of 'shadowmap' and similar to 'shadow map'.

It should also be very fast to render shadows using openGL. Shadowmaps are a standard technique for rendering dynamic shadows. In shadowmapping, a scene is rendered from the perspective of a point light source and the resulting ``image'' is colored according to how far each part of the image is from the light. Shadowmapping typically goes on to use this information to shade a rendering of the same scene from another perspective, but we only want an image of the shadow on the wall. Therefore we would instead iterate over the pixels in the image and compare the depth of each to the calculated depth at the relevant point in the shadow map. If the depths match to within some approximation then that pixel is unshadowed, and inversely, if they differ, the pixel is shadowed. That this lighting method is dynamic is advantageous because the shadow will have to be rendered with respect to multiple point light sources. Like the first method, this method has the downside of requiring that the shadows from each light be averaged.

@@

The simplest method of representing nodes and edges would be to keep the number of both constant, moving the nodes around while retaining the same edge mappings for all genomes.  This way, one could represent each node as an unsigned integer, or an array of three unsigned integers representing the positive incremental distance from some origin point.  Given the nature of the problem, one can disregard any space not within the projection from the light source to a given section of the wall.  This allows the bounding of the entire system in a cube, which we can use to define our \texttt{0} and our \texttt{MAX\_INT} for each coordinate direction.  Next, we would create an array of unsigned integers, of length 3 times the number of nodes in the system.  This would be the genome for the genetic algorithm.  The fitness function would be defined as the number of matching pixels (within a certain threshold) between the input and the generated shadow using one of the shadowmapping methods above.  Using such a method would prevent situations where the graph became unconnected, but it does not address issues of structural integrity any further than this.  Since the nature of the problem allows for many local solutions, the ability of such a genetic algorithm to converge may be slowed.

>>>>

It should also be very fast to render shadows using openGL. Shadow maps are a standard technique for rendering dynamic shadows. In shadow mapping, a scene is rendered from the perspective of a point light source and the resulting ``image'' is colored according to how far each part of the image is from the light. Shadow mapping typically goes on to use this information to shade a rendering of the same scene from another perspective, but we only want an image of the shadow on the wall. Therefore we would instead iterate over the pixels in the image and compare the depth of each to the calculated depth at the relevant point in the shadow map. If the depths match to within some approximation then that pixel is unshadowed, and inversely, if they differ, the pixel is shadowed. That this lighting method is dynamic is advantageous because the shadow will have to be rendered with respect to multiple point light sources. Like the first method, this method has the downside of requiring that the shadows from each light be averaged.

@@

The simplest method of representing nodes and edges would be to keep the number of both constant, moving the nodes around while retaining the same edge mappings for all genomes.  This way, one could represent each node as an unsigned integer, or an array of three unsigned integers representing the positive incremental distance from some origin point.  Given the nature of the problem, one can disregard any space not within the projection from the light source to a given section of the wall.  This allows the bounding of the entire system in a cube, which we can use to define our \texttt{0} and our \texttt{MAX\_INT} for each coordinate direction.  Next, we would create an array of unsigned integers, of length 3 times the number of nodes in the system.  This would be the genome for the genetic algorithm.  The fitness function would be defined as the number of matching pixels (within a certain threshold) between the input and the generated shadow using one of the shadow mapping methods above.  Using such a method would prevent situations where the graph became unconnected, but it does not address issues of structural integrity any further than this.  Since the nature of the problem allows for many local solutions, the ability of such a genetic algorithm to converge may be slowed.
